Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-10 Paper/paper.tex
Have added image with both plots on together
Have removed the indexing of the states - this was not needed

In total there are $(c_{\NH}+1)\times(c_{\RG}+1)$ states and they are indexed lexicographically: $(0,0), (0,1), (0,2)$, etc. In general, state $(u,v)$ is the $s(u,v)th$ state where $s(u,v)=u(c_{\RG}+1)+(v+1)$.

@@

\begin{figure}[!htbp]
$$\begin{array}{cc}
\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_NH.pdf}&
\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_RG.pdf}
\end{array}$$
\caption{Plots of $f_{\NH}(K_{\RG})$ and $f_{\RG}(K_{\NH})$}\label{exampleforproof}
\end{figure}

>>>>

In total there are $(c_{\NH}+1)\times(c_{\RG}+1)$ states and they are indexed lexicographically: $(0,0), (0,1), (0,2), \dots$.

@@

\begin{figure}[!htbp]
    \begin{center}
        \includegraphics[width=.7\textwidth]{./Images/best_responses_ex_for_proof.pdf}
    \end{center}
    \caption{Plots of $f_{\NH}(K_{\RG})$ and $f_{\RG}(K_{\NH})$}\label{exampleforproof}
\end{figure}
